---
title: "Participation Assignment 2 - Employee Reviews"
author: "Evan Buss, Aaron Raff"
date: "February 12, 2019"
due: "February 17, 2019"
output: html_document
---

## Question
### Do former employees give lower company ratings than current employees?

```{r}
library(dplyr)
# Load data set
employeeData <- read.csv("employeeReviews.csv", stringsAsFactors = FALSE)
```


### Group data set based on the reviewers employment status.
```{r}
# Group the reviews based on whether it is from a current employee or a former employee
employeeStatus <- employeeData %>% group_by(grepl("Current Employee", job.title))
```

### Create a dataframe containing the mean of each star rating given by both current and former employees
```{r}
results <- suppressWarnings(data.frame(
  status=c("Former Employees", "Current Employees"),
  summarise(employeeStatus, reviews=n())[2],
  round(summarise(employeeStatus, overall = mean(as.numeric(overall.ratings)))[2], digits = 2),
  round(summarise(employeeStatus, workBalance = mean(as.numeric(work.balance.stars), na.rm = TRUE))[2], digits = 2),
  round(summarise(employeeStatus, culture = mean(as.numeric(culture.values.stars), na.rm = TRUE))[2], digits = 2),
  round(summarise(employeeStatus, opportunities = mean(as.numeric(carrer.opportunities.stars), na.rm = TRUE))[2], digits = 2),
  round(summarise(employeeStatus, benefits = mean(as.numeric(comp.benefit.stars), na.rm = TRUE))[2], digits = 2),
  round(summarise(employeeStatus, management = mean(as.numeric(senior.mangemnet.stars), na.rm = TRUE))[2], digits = 2)
))

print(results)
```

### Plot the results
```{r}
bplot <- barplot(as.matrix(results[,c(-1,-2)]), 
                 main="Average Current vs Former Employee Reviews", 
                 xlab="Company Rating Category", 
                 col=c("red3","deepskyblue"), 
                 ylab = "Average Number of Stars",
                 legend = c("Former Employees", "Current Employees"),
                 args.legend = list(x="topright", bty='n'),
                 ylim=c(0,5), beside=TRUE, xpd = FALSE)
```

### Results
As you can see the grouped bar plot shows that, on average, former employees give lower ratings than current employees.